\documentclass[12pt]{article}
\usepackage[colorlinks=true, linkcolor=blue, breaklinks=true]{hyperref} 
\usepackage{graphicx}
\usepackage[euler-digits]{eulervm}
\usepackage{charter,amsmath,amssymb,breakurl}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{multicol}
\everymath{\displaystyle}
\author{}\date{}
\title{Math 104 Review Problems for Exam 3}\author{}
\begin{document}
\maketitle
\pagestyle{empty}
\begin{enumerate}
\item Do exercises~43--57 of the Review Exercises
on page 97~of your textbook.
The answers to all these exercises are in the
back of the book on page~104.

\item This exercise concerns the game of craps.
\begin{enumerate}
\item What is the probability of throwing a craps? That is, what is
the probability of rolling a sum of 2, 3, or 12 with two dice?
\item What is the probability of rolling a sum of~10 with two dice?
\item Suppose you roll a sum of 10 on your initial craps roll.
At this stage, what is the probability that you will win the game?
\item What is the probability of rolling a sum of~10 on the initial
roll {\bf and} subsequently winning the game?
\end{enumerate}

\item
Two cards are drawn at random from a deck of playing cards
without replacement.
\begin{enumerate}
\item What is the probability that both cards have suit
$\heartsuit$?
\item What is the probability that the second card has
suit $\heartsuit$
given that the first card has suit $\heartsuit$?
\item What is the probability that the second card has
suit $\heartsuit$
given that the first card has suit $\diamondsuit$?
\item What is the probability that the second card has
suit $\heartsuit$
and the first card has suit $\diamondsuit$?
\end{enumerate}

\item The following table shows the number
of respondents to the American Community
Survey living in Iowa,
organized by race and foodstamp usage (SNAP) over the past 12~months.
\footnote{Source: \tt www.census.gov}
\[\begin{array}{l|rr|r}
&\text{Received SNAP}&\text{Didn't receive SNAP}
&\text{Total}\\\hline
\text{White}&115,248&1,037,390&1,152,638\\
\text{African American}&12,360&18,056&30,416\\
\text{American Indian}&1099&2,160&3,259\\
\text{Asian}&1913&15,200&17,113\\
\text{Pacific Islander}&86&209&295\\
\text{Hispanic}&9424&30,248&39,672\\
\text{Other race}&2996&8457&11,453\\
\text{Several races}&3615&7758&11,373\\\hline
\text{Total}&137,317&1,089,230&1,226,547
\end{array}\]
\begin{enumerate}
\item How many respondents received food stamps over the
past 12~months?
\item What is the probability that a randomly selected
respondent did not receive food stamps given that
the respondent is Asian?
\item What is the probability that a randomly selected
respondent is white given that the respondent
received food stamps?
\item How many respondents received food stamps and
are not white?
\item What is the probability that a randomly selected
respondent was of several races?
\item How many African American respondents received
food stamps?
\item What is the probability that a randomly selected
respondent received food stamps?
\end{enumerate}
\end{enumerate}

\noindent{\bf Answers:}
\begin{enumerate}
\item See page 104 of your textbook.
\item $\frac{1}{9}$,\quad $\frac{1}{12}$,\quad $\frac{1}{3}$,
\quad $\frac{1}{36}$
\item $\frac{13}{52}\cdot\frac{12}{51}$,\quad
$\frac{12}{51}$,\quad $\frac{13}{51}$,\quad
$\frac{13}{52}\cdot\frac{13}{51}$
\item\begin{enumerate}
\item $137,317$
\item $\frac{15200}{17113}$
\item $\frac{115248}{137317}$
\item $22,069$
\item $\frac{11373}{1226547}$
\item $12,360$
\item $\frac{137317}{1226547}$
\end{enumerate}
\end{enumerate}


\end{document}
