\documentclass[12pt]{article}
\usepackage[colorlinks=true, linkcolor=blue, breaklinks=true]{hyperref} 
\usepackage{graphicx}
\usepackage[euler-digits]{eulervm}
\usepackage{charter,amsmath,amssymb,breakurl}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{multicol}
\everymath{\displaystyle}
\author{}\date{Due in class Friday 6 February}
\title{Math 104 Written Assignment 1}\author{}
\begin{document}
\maketitle
\pagestyle{empty}
\begin{enumerate}
\item Marcus and Andrew are playing rock-paper-scissors
for money as follows. Both players select and simultaneously display
one of three gestures, rock, paper, or scissors.
If the two players select the same gesture, then Marcus pays Andrew 
$\$3$. If they select different gestures, then Andrew pays Marcus $\$1$.
\begin{enumerate}
\item List all the possible outcomes of the part of the game
where the two players select gestures.
\vspace{.6in}
\item Calculate the expected proceeds for Marcus.
\vspace{.6in}
\item Calculate the expected proceeds for Andrew.
\vspace{.6in}
\item How can the payments be changed so that game favors Marcus?
\vspace{.6in}
\item How can the payments be changed so that game is fair to both
players?
\vspace{.6in}
\item How can payments be introduced into the
\href{http://en.wikipedia.org/wiki/Rock-paper-scissors}{standard rules}
in such a way that the game will be fair to both players?
\end{enumerate}
\newpage

\item An insurance company sells a $\$100,000$
life insurance policy for $\$2000$. 
In other words, a customer pays the company $\$2000$;
if the customer dies within one year, then the company
pays the customer's estate $\$100,000$ but keeps the $\$2000$;
if the customer survives for one year, then
the company pays the customer nothing and keeps the $\$2000$. 
Suppose that the probability of a $30$~year old woman surviving
for one year is $0.985$.
\begin{enumerate}
\item What is the expected revenue for the insurance company?
\vspace{2in}
\item What is the {\em minimum} amount $P$ the
company should charge her for a $\$100,000$ life
insurance policy in order
for the company to profit in the long run?
\end{enumerate}
\end{enumerate}
\end{document}
