\documentclass[12pt]{article}
\usepackage{eulervm}
\usepackage{charter,amsmath,amssymb,breakurl}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{multicol}
\everymath{\displaystyle}
\author{}\date{Due in class Monday 20 October}
\title{Math 104 Worksheet 6}\author{}
\begin{document}
\maketitle
\thispagestyle{empty}

The Inclusion-Exclusion Theorem for three sets $E,F,G$ reads
\[\left|E\cup F\cup G\right|
=\left|E\right|+\left|F\right|+\left|G\right|
-\left|E\cap F\right|
-\left|E\cap G\right|
-\left|F\cap G\right|
+\left|E\cap F\cap G\right|\]
Use the Inclusion-Exclusion Theorem to answer the following questions.
\begin{enumerate}
\item Use a Venn Diagram to explain why
the Inclusion-Exclusion Theorem is true.
\vspace{.5in}
\item The music program at Ames High School
consists of band, orchestra, and chorus. There are
$5$ students in all three ensembles.
There are $5$ in both band and orchestra, $9$
in both orchestra and chorus, and $8$ in both band
and chorus. Finally, there are $61$ students in band,
$72$ in orchestra, and $83$ in chorus. How many students
altogether are in the music program at Ames High School?
\vspace{1in}
\item In this exercise we
will calculate the probability of winning
Chuck-a-luck using the Inclusion-Exclusion formula.
Suppose you bet $\$1$ on the number 6.
This means that you win $\$1$, $\$2$, or $\$3$ 
if one, two, or three dice respectively show 6.
Let $E$ be the event that the first die shows 6.
Let $F$ and $G$ be the events that the second
and third die respectively shows 6.
You will want to use a Venn diagram to organize the
information in this exercise.
\begin{enumerate}
\item List all the outcomes in $E\cap F\cap G$.
\vspace{.5in}
\item List all the outcomes in $E\cap F$.
\vspace{.5in}
\item How many outcomes are in $E\cap F\cap G'$?
Write this number in the appropriate region of your
Venn diagram.
\item Similarly, write $\left|E\cap F'\cap G\right|$
and $\left|E'\cap F\cap G\right|$ in your Venn diagram.
You need not list the elements of $E\cap F'\cap G$
or $E'\cap F\cap G$.
\item List all the outcomes in $E\cap F'\cap G'$.
Note that none of these elements have been listed above.
Write $\left|E\cap F'\cap G'\right|$ in your Venn diagram.
\vspace{1in}
\item Similarly, write
$\left|E'\cap F\cap G'\right|$
and $\left|E'\cap F'\cap G\right|$ in 
the appropriate regions of your Venn diagram.
You need not list the elements of
$E\cap F'\cap G'$ or $E'\cap F'\cap G$.
\item Use your Venn diagram to calculate
$\left|E\right|$. How could you have used
the Counting Principle to calculate this number?
\vspace{.5in}
\item Use the Inclusion-exclusion formula
or your Venn diagram to calculate
$\left|E\cup F\cup G\right|$.
\vspace{.5in}
\item Calculate the probability of winning
Chuck-a-luck using your calculations above.
\end{enumerate}
\end{enumerate}
\end{document}
