\documentclass[12pt]{article}
\usepackage{charter,amsmath,amssymb,breakurl}
\usepackage{eulervm}
\usepackage[letterpaper,margin=.8in]{geometry}
\usepackage{multicol}
\everymath{\displaystyle}
\author{}
\title{Math 104 Worksheet 7 Solutions}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{enumerate}
\item Calculate the value of each of the following
initial farkle rolls.
\begin{enumerate}
\item $1,1,2,3,5,6$
\qquad{\bf Answer:} 250
\item $1,1,1,2,2,3$
\qquad{\bf Answer:} 1000
\item $2,2,3,3,5,5$
\qquad{\bf Answer:} 750
\item $2,2,2,2,3,5$
\qquad{\bf Answer:} 450
\item $1,2,3,4,5,6$
\qquad{\bf Answer:} 1500
\end{enumerate}

\item Suppose you are playing farkle with your
friends. You initially roll $1,2,2,2,5,6$.
\begin{enumerate}
\item\label{Stay}
According to the rules, can you end your turn now?
Explain why or why not.\\
{\bf Answer:} Yes, because the roll is worth 350~points,
which is greater than 300~points.
\item One possible choice is to reroll the die showing 6.
Calculate your expected winnings for this turn in
this situation.
This means that you should list all the possible {\em net}
outcomes, multiply each outcome by its probability,
and add the results.

{\bf Solution:} The following table shows
all the possible outcomes.
\[\begin{array}{ccc}
\text{Roll}&\text{Probability}&\text{Net outcome}\\\hline
1&1/6&450\\
5&1/6&400\\
2,3,4,6&2/3&0
\end{array}\]
The expected winnings are therefore
$\frac{1}{6}\left(450\right)+\frac{1}{6}\left(400\right)
\approx 142$.

\item\label{RollTwo} Another possible choice is to reroll
the dice showing $5,6$.
Calculate your expected winnings for this turn in
this situation.

{\bf Solution:} The following table shows
all the possible outcomes, where
the wildcards $x$ and $y$ denote one of the numbers
$2,3,4,6$.
\[\begin{array}{ccc}
\text{Roll}&\text{Probability}&\text{Net outcome}\\\hline
\left(1,1\right)&1/36&500\\
\left(5,5\right)&1/36&400\\
\left(1,5\right),\left(5,1\right)&2/36&450\\
\left(1,x\right),\left(x,1\right)&8/36&400\\
\left(5,x\right),\left(x,5\right)&8/36&350\\
\left(x,y\right)&16/36&0\\
\end{array}\]
Thus the expected winnings are
\[\frac{1}{36}\left(\rule{0pt}{12pt}
1\left(500\right)+1\left(400\right)
+8\left(400\right)+2\left(450\right)
+8\left(350\right)\right)\approx 217\]

\item Using your results above, decide which
choice you should make.

{\bf Answer:} Of the three possibilities proposed in
parts~(\ref{Stay})--(\ref{RollTwo}) the move
with the highest expectation is (\ref{Stay}), namely,
to reroll none of the dice. In fact,
there are several possible moves not shown here, and 
rerolling no dice has the highest expectation among
all possible moves.
\end{enumerate}
\end{enumerate}
\end{document}
